3.4: Examples

### 2019-10-31 static/slides/16-slides.Rmd
Tweak slides 16 formatting

.center[
![](https://www.dropbox.com/s/bfw0v2wqnqw3j89/sacerdote3.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/ull5y5x691hn54r/sacerdote3c.png?raw=1)
]

@@

.class: inverse, center, middle
# Duggan and Levitt (2002) on Corruption in Sumo Wrestling

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/iu3ua5wbh2ulv0d/sumo.jpg?raw=1)
]
]
.source[Duggan, Mark and Steven D. Levitt, (2002), "Winning isn't Everything: Corruption in Sumo Wrestling" *American Economic Review* 92(5):1594-1605]

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/23hzngfz77h7rtb/sumo1.png?raw=1)
]
]
.source[Duggan, Mark and Steven D. Levitt, (2002), "Winning isn't Everything: Corruption in Sumo Wrestling" *American Economic Review* 92(5):1594-1605]

@@

.center[
![](https://www.dropbox.com/s/bamwd6eq97rugou/sumo4.png?raw=1)

@@

.pull-left[
.center[
![](https://www.dropbox.com/s/qnh3i0pwogiz1y6/sumo5.png?raw=1)
]
]

@@

.center[
![](https://www.dropbox.com/s/z2l381t0yqaykki/sumo6.png?raw=1)
]

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/92fk22dz2zctozu/rentseeking.png?raw=1)
]
]
.source[Fisman, Raymond and Edward Miguel, (2007), "Corruption, Norms, and Legal Enforcement: Evidence from Diplomatic Parking Tickets," *Journal of Political Economy* 115(6): 1020-1048]

@@

.center[
![](https://www.dropbox.com/s/5ndr02pwjvv6zr3/parking2.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/izkvkpu2izi78sr/parking3.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/rf6r3g66u3aaulr/parking4.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/2drdlc105j2i15m/parking7.png?raw=1)
]

@@

.center[
![](https://www.dropbox.com/s/t1s9e3xb3kkn428/parking5.png?raw=1)
]

>>>>

.center[
![:scale 40%](https://www.dropbox.com/s/bfw0v2wqnqw3j89/sacerdote3.png?raw=1)
]

@@

.center[
![:scale 40%](https://www.dropbox.com/s/ull5y5x691hn54r/sacerdote3c.png?raw=1)
]

@@

class: inverse, center, middle
# Duggan and Levitt (2002) on Corruption in Sumo Wrestling

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/iu3ua5wbh2ulv0d/sumo.jpg?raw=1)
]
]

.source[Duggan, Mark and Steven D. Levitt, (2002), "Winning isn't Everything: Corruption in Sumo Wrestling" *American Economic Review* 92(5):1594-1605]

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/23hzngfz77h7rtb/sumo1.png?raw=1)
]
]

.source[Duggan, Mark and Steven D. Levitt, (2002), "Winning isn't Everything: Corruption in Sumo Wrestling" *American Economic Review* 92(5):1594-1605]

@@

.center[
![:scale 70%](https://www.dropbox.com/s/bamwd6eq97rugou/sumo4.png?raw=1)

@@

.pull-left[
.center[
![:scale 60%](https://www.dropbox.com/s/qnh3i0pwogiz1y6/sumo5.png?raw=1)
]
]

@@

.center[
![:scale 60%](https://www.dropbox.com/s/z2l381t0yqaykki/sumo6.png?raw=1)
]

@@

.pull-right[
.center[
![](https://www.dropbox.com/s/92fk22dz2zctozu/rentseeking.png?raw=1)
]

@@

.center[
![:scale 70%](https://www.dropbox.com/s/5ndr02pwjvv6zr3/parking2.png?raw=1)
]

@@

.center[
![:scale 50%](https://www.dropbox.com/s/izkvkpu2izi78sr/parking3.png?raw=1)
]

@@

.center[
![:scale 40%](https://www.dropbox.com/s/rf6r3g66u3aaulr/parking4.png?raw=1)
]

@@

.center[
![:scale 70%](https://www.dropbox.com/s/2drdlc105j2i15m/parking7.png?raw=1)
]

@@

.center[
![:scale 70%](https://www.dropbox.com/s/t1s9e3xb3kkn428/parking5.png?raw=1)
]
